---
title: "HWK2"
author: "shannon jaskiewicz"
date: '2022-09-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Looking at the Boston dataset from the MASS package in R---examining crime rate as a function of various predictors:**  


zn---proportion of residential land zoned for lots < 25k sqft
indus---proportion of non-retail business acres per town
rm---avg num rooms per dwelling
age---proportion of owner-occupied units built before 1940
dis---weighted mean of distances to 5 Boston job centers
rad---index of accessibility to radial highways
ptratio---pupil-teacher ratio
lstat---lower socioeconomic status
medv---median value of owner-occupied homes in thousands of dollars


**Getting a correlation plot**

```{r, warning = FALSE, message = FALSE}

library(tidyverse)
library(corrplot)
library(plotly)
library(htmlwidgets)
library(heatmaply)
library(MASS)

# help(Boston)


boston <- Boston[-c(4,5,10,12)]
boston.htmplycor <- heatmaply_cor(
  cor(boston),
  symm = TRUE,
  dendrogram = "none"
)
boston.htmplycor
```


**Linear regression with crime rate as the outcome variable**

```{r}
lm.boston <- lm(crim ~ ., data = boston)
summary(lm.boston)
# confint(lm.boston)
# coef(lm.boston)
results <- data.frame(confint(lm.boston),coef(lm.boston))
colnames(results) = c("Lower CI", "Upper CI", "Estimate")
results2 <- results[-1,]
results2$name <- substr(rownames(results2), 1,9)
results2$sig <- (results2$`Lower CI` > 0 | results2$`Upper CI` < 0)
results2
```


**Making the ggplot**

```{r}
boston.ggp <- ggplot(results2,
                     aes(x = Estimate,
                         y = name,
                         xmin = `Lower CI`,
                         xmax = `Upper CI`,
                         color = sig)) +
  geom_vline(xintercept = 0,
             color = "black",
             linetype = 2) +
  geom_errorbarh(height = 0.25) +
  geom_point() +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  #scale_x_continuous(breaks = seq(-21,2,0.1)) +
  scale_color_manual(values = c("black","red"))
# boston.ggp
```


**Converting it to plotly**

```{r}
boston.ggp.plotly <- ggplotly(boston.ggp, tooltip = c("Lower CI", "Estimate", "Upper CI"))
boston.ggp.plotly
```



**Combining the 2 plots, side by side, into 1 plot **

```{r, fig.width = 10, fig.height = 5, warning = FALSE}
boston.htmplycor2 <- boston.htmplycor %>%
  layout(
    yaxis = list(showticklabels = FALSE)
  )
boston.combo <- subplot(list(boston.ggp.plotly,boston.htmplycor2),
                       margin = 0.03,
                       nrows = 1,
                       widths = c(0.5,0.5))
boston.combo
```




**Saving the plot**

```{r}

saveWidget(as_widget(boston.combo), "boston.combo.html")
save(boston.combo, file="boston.combo.rda")
```

